Component-based Software Development Framework \\for Embedded IoT Devices（仮）

### 2017-11-14 ipsj/paper.tex
Update Introduction
Add contributions

This paper proposes an extended framework of mruby on TECS that can be applied to embedded network software development for IoT devices.
In the proposed framework, a component-based TCP/IP protocol stack, TINET+TECS, is comprised, and it is possible to utilize TINET function from mruby programs.

TINET is a compact TCP/IP protocol stack for embedded systems \cite{url:TINET}.
TINET comprises many complex source codes, i.e., it contains many files and defines many macros, which can be problematic for software developers seeking to maintain, extend, and analyze the software.
TINET+TECS is a componentized TIENT with TECS to improve the configurability and scalability of TCP/IP software.

In addition, this paper proposes a component-based dynamic memory allocator, TLSF+TECS. 
TLSF is a dynamic memory allocator for real-time systems, which can always run with $O(1)$ and improve memory usage efficiency by deviding memory blocks in two stages.
In the current version of TLSF, memory contention may occur when multiple threads run at the same time.
TLSF+TECS is a componentized TLSF memory allocator, which can be thread-safe allocator because each component has its own heap area.

{\bf Contributions}: The proposed framework provides the following contributions.
\begin{enumerate}
\item {\bf :}
\item {\bf :}
\item {\bf :}
\item {\bf :}
\end{enumerate}

>>>>

This paper proposes an extended framework of mruby on TECS that can be applied to embedded network software development for IoT devices.
In the proposed framework, a component-based TCP/IP protocol stack, TINET+TECS, is comprised, and it is possible to utilize TINET function from mruby programs.
TINET is a compact TCP/IP protocol stack for embedded systems \cite{url:TINET}.
TINET comprises many complex source codes, i.e., it contains many files and defines many macros, which can be problematic for software developers seeking to maintain, extend, and analyze the software.
TINET+TECS is a componentized TIENT with TECS to improve the configurability and scalability of TCP/IP software.
In the case of only sending values obtained by sensors, it is better to custimize easily, such as removing unused functions.
The improved configurability leads to satisfy strict memory constrains of embedded systems.
In addition, this paper proposes a component-based dynamic memory allocator, TLSF+TECS. 
TLSF is a dynamic memory allocator for real-time systems, which can always run with $O(1)$ and improve memory usage efficiency by deviding memory blocks in two stages.
In the current version of TLSF, memory contention may occur when multiple threads run at the same time.
TLSF+TECS is a componentized TLSF memory allocator, which can be thread-safe allocator because each component has its own heap area.

{\bf Contributions}: The proposed framework provides the following contributions.
\begin{enumerate}
\item {\bf Applicable to various devices:}
The proposed framework does not depend on RTOSs or hardware, it can be utilized in various devices.
mruby code is portable, so it is possible to run the same program on different devices.

\item {\bf Improve configurability:}
Because TINET+TECS is a component-based system, its software can flexibly change as system's configuration by, for example, resizing network buffer, adding/removing TCP (or UDP) functionality, or supporting either IPv4 or IPv6.
In addition, the use by TINET+TECS of individual component diagrams enables visualization of an entire system.

\item {\bf Thread-safe memory allocator:}
TLSF+TECS runs thread safely without exclusive control even if multiple threads operate in parallel.
Moreover, each thread can easily set its own heap area.

\end{enumerate}
